Project proposal: Explanations for unexplained effect size heterogeneity

### 2023-05-21 code/tables.qmd
tables: removed table 2 version 2

positive_bias_table <- table1 %>%
         knitr::kable(booktabs = T, escape = FALSE, digits = 2,
          col.names = c("Meta-Analysis",
                        "$\\rho_{xy}$",
                        "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6",
                        "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7",
                        "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8",
                        "SD(ES)")) %>%
  kable_styling(position = "left") %>%
  add_header_above(c(" " = 2, "Study 1"= 1, "Study 2" = 1, "Study 3" = 1)) %>%
  add_header_above(c(" " = 2, "Observed Effect Sizes" = 3)) %>%
  footnote(general = "Reproduced from Olsson Collentine et al. (2020). The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ and the true effect size $\\\\rho_{xy}$ when within-study sample size is infinite. SD (ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III, equivalent to heterogeneity given infinite within-study sample sizes. Code to reproduce table: LINK",
  threeparttable = TRUE, escape = FALSE, footnote_as_chunk = TRUE)

@@

## Table 2 (version 1)
### Imperfect reliability leads to negative bias in heterogeneity estimates

@@

dat %>% knitr::kable(booktabs = TRUE, escape = FALSE, digits = 2,
                    align=rep('c', 5),
 col.names = c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$",
               "Study 1",
               "Study 2",
               "Study 3",
               "SD(ES)")) %>%
 kable_styling(position = "left") %>%
 add_header_above(c(" " = 1, "Observed Effect Sizes" = 3)) %>%
 footnote(general = "The values under Study 1, 2 and 3 are observed effect sizes for that study given the measurement reliability $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ and the true effect size of that study (first row) when within-study sample size is infinite. SD (ES) is the standard deviation of the observed effect sizes, equivalent to heterogeneity given infinite within-study sample sizes. Code to reproduce table: LINK",
  threeparttable = TRUE, escape = FALSE, footnote_as_chunk = TRUE)
```

## Table 2 (version 2)
### Imperfect reliability leads to negative bias in heterogeneity estimates

```{r, alternative negative bias table}
#Alternative table
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = 1",
         "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = 0.8",
         "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = 0.6")

dat <- cbind(rel, r, sds)

negative_bias_table <- dat %>%
            knitr::kable(booktabs = TRUE, escape = FALSE, digits = 2,
            col.names = c("",
                        "Study 1",
                        "Study 2",
                        "Study 3",
                        "SD(ES)")) %>%
            kable_styling(position = "left") %>%
            add_header_above(c(" " = 1, "Observed Effect Sizes" = 3)) %>%
            column_spec (1, border_right = FALSE) %>%
            footnote(general = "The values under Study 1, 2 and 3 are observed effect sizes for that study given the measurement reliability $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ and the true effect size of that study (first row) when within-study sample size is infinite. SD (ES) is the standard deviation of the observed effect sizes, equivalent to heterogeneity given infinite within-study sample sizes. Code to reproduce table: LINK",
  threeparttable = TRUE, escape = FALSE, footnote_as_chunk = TRUE)

@@

saveRDS(list(positve_bias_table = positive_bias_table,
             negative_bias_table = negative_bias_table),
        "../manuscript/tables.RDS")
```

>>>>

positive_bias_table <- table1 %>%
         knitr::kable(booktabs = T, escape = FALSE, digits = 2,
          col.names = c("Meta-Analysis",
                        "$\\rho_{xy}$",
                        "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6",
                        "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7",
                        "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8",
                        "SD(ES)")) %>%
  kable_styling(position = "left") %>%
  add_header_above(c(" " = 2, "Study 1"= 1, "Study 2" = 1, "Study 3" = 1)) %>%
  add_header_above(c(" " = 2, "Observed Effect Sizes" = 3)) %>%
  footnote(general = "Reproduced from Olsson Collentine et al. (2020). The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ and the true effect size $\\\\rho_{xy}$ when within-study sample size is infinite. SD (ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III, equivalent to heterogeneity given infinite within-study sample sizes. As true heterogeneity is absent, any SD(ES) values above zero represent bias. Code to reproduce table: LINK",
  threeparttable = TRUE, escape = FALSE, footnote_as_chunk = TRUE)

@@

## Table 2
### Imperfect reliability leads to negative bias in heterogeneity estimates

@@

negative_bias_table <- dat %>%
 knitr::kable(booktabs = TRUE, escape = FALSE, digits = 2,
                    align=rep('c', 5),
 col.names = c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$",
               "Study 1",
               "Study 2",
               "Study 3",
               "SD(ES)")) %>%
 kable_styling(position = "left") %>%
 add_header_above(c(" " = 1, "Observed Effect Sizes" = 3)) %>%
 footnote(general = "The values under Study 1, 2 and 3 are observed effect sizes for that study given the measurement reliability $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ and the true effect size of that study (first row) when within-study sample size is infinite. SD (ES) is the standard deviation of the observed effect sizes, equivalent to heterogeneity given infinite within-study sample sizes. Code to reproduce table: LINK",
  threeparttable = TRUE, escape = FALSE, footnote_as_chunk = TRUE)

@@

saveRDS(list(positive_bias_table = positive_bias_table,
             negative_bias_table = negative_bias_table),
        "../manuscript/tables.RDS")
```
